E~2~: Civil society environment predicts deteriorating human rights

### 2021-11-19 analysis/01_data-overview.Rmd
Remove REWB stuff
Remove all civlib and clphy models

  tar_load(skeleton)
  tar_load(chaudhry_clean)
  tar_load(pts_clean)
  tar_load(latent_hr_clean)
  tar_load(killings_all)
  tar_load(vdem_clean)
  tar_load(wdi_clean)
  tar_load(un_pop)
  tar_load(un_gdp)
  tar_load(ucdp_prio_clean)

@@

## Gohdes and Carey journalist deaths

We use data from [Gohdes and Carey (2017)](https://doi.org/10.1177/0022343316680859) for the number of journalists murdered between 2002 and 2014. They provide two `.Rdata` files in their replication materials—one is a list of all journalist deaths, and one is a TSCS dataset they use in their main analysis, with summary values of journalist deaths for each country/year. Their panel data does not include 2002 for some reason, so we ignore the panel data and recreate the summary values by hand here.

```{r glimpse-gh-journalists}
glimpse(killings_all)
```

@@

There are only a tiny handful of rows with missing data: Serbia pre-2006.

@@

There are just two instances of missing data with PTS scores:

>>>>

  tar_load(skeleton)
  tar_load(chaudhry_clean)
  tar_load(pts_clean)
  tar_load(latent_hr_clean)
  tar_load(vdem_clean)
  tar_load(wdi_clean)
  tar_load(un_pop)
  tar_load(un_gdp)
  tar_load(ucdp_prio_clean)

@@

@@

There are only a tiny handful of rows with missing NGO law data: Serbia pre-2006 and Russia pre-1992

@@

There are a handful of instances of missing data with PTS scores:

### 2021-11-19 analysis/02_descriptive-analysis.Rmd
Remove all civlib and clphy models

```{r model-pts-cs, message=FALSE, results="hide"}
diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_pts")
)
```

@@

diff_cs_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_predicted_draws(diff_cs_pts, seed = BAYES_SEED)
```

```{r plot-draws-pts-cs}
ggplot(diff_cs_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  stat_halfeye() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-cs, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

## Chaudhry NGO regulations and the PTS

```{r model-pts-restrictions, message=FALSE, warning=FALSE, results="hide"}
diff_ngo_pts <- brm(
  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = select(canary, barriers_total, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_ngo_pts")
)
```

```{r draws-pts-ngo}
diff_ngo_pts_summary <- diff_ngo_pts %>%
  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
  median_hdci(.width = 0.95) %>% 
  to_broom_names()

diff_ngo_pts_draws <- diff_ngo_pts %>% 
  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
  ungroup() %>% 
  mutate(.variable = str_replace(.variable, "b_PTS_factorLevel", "Level ")) %>% 
  mutate(pts_level = fct_rev(.variable))

diff_ngo_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_predicted_draws(diff_ngo_pts, seed = BAYES_SEED)
```

```{r plot-draws-pts-ngo}
ggplot(diff_ngo_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  stat_halfeye() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-ngo, warning=FALSE, message=FALSE}
ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

# Conflict and civil society restrictions

```{r model-conflict-cs, message=FALSE, results="hide"}
diff_cs_conflict <- brm(
  bf(v2csreprss ~ 0 + armed_conflict, sigma ~ 0 + armed_conflict),
  family = student,
  data = select(canary, v2csreprss, armed_conflict),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_conflict")
)
```

```{r draws-conflict-cs}
diff_cs_conflict_summary <- diff_cs_conflict %>%
  gather_draws(`b_armed.*`, regex = TRUE) %>% 
  median_hdci(.width = 0.95) %>% 
  to_broom_names()

diff_cs_conflict_draws <- diff_cs_conflict %>% 
  gather_draws(`b_armed.*`, regex = TRUE) %>% 
  ungroup() %>% 
  mutate(.variable = recode(.variable, `b_armed_conflictFALSE` = "No armed conflict",
                            `b_armed_conflictTRUE` = "Armed conflict"))

diff_cs_conflict_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(armed_conflict) %>% 
  add_predicted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
  ungroup() %>% 
  mutate(armed_conflict = factor(armed_conflict, labels = c("No armed conflict", "Armed conflict")))
```

```{r plot-draws-conflict-cs}
ggplot(diff_cs_conflict_draws, aes(y = .variable, x = .value, fill = .variable)) + 
  stat_halfeye() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict") +
  theme_ngo()
```

```{r plot-posterior-preds-conflict-cs, warning=FALSE, message=FALSE}
ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

>>>>

```{r model-pts-cs, message=FALSE, results="hide"}
diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED
)
```

@@

diff_cs_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_epred_draws(diff_cs_pts, seed = BAYES_SEED)
```

```{r plot-draws-pts-cs}
ggplot(diff_cs_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  stat_halfeye() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = "none") +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-cs, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .epred, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dots(quantiles = 100, shape = 19) +
  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = "none") +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

### 2021-11-19 analysis/03_environment-repression.Rmd
Remove all civlib and clphy models

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(broom.mixed)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(here)

@@

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
             m_clphy_baseline, m_clphy_v2csreprss, 
             m_clpriv_baseline, m_clpriv_v2csreprss, 
             m_lhr_baseline, m_lhr_v2csreprss))

  # Load regression tables
  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c, models_tbl_e2d))

@@

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

# E~2b~: Civil society environment and physical violence

```{r tbl-e2b}
# Build nicer column names
models_for_table_e2b <- models %>% 
  filter(outcome_var == "Physical violence") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

@@

```{r plot-coefs-e2b}
coef_plots <- models %>% 
  filter(model == "m_clphy_v2csreprss") %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

```{r plot-mfx-e2b}
mfx <- models %>% 
  filter(model == "m_clphy_v2csreprss") %>% 
  mutate(plot_vars = "v2csreprss") %>% 
  mutate(fx = map2(actual_model, plot_vars, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Civil society repression\n(higher values = less repression)",
       y = "Predicted physical violence index\n(higher values = less violence)") +
  theme_ngo()
```

# E~2c~: Civil society environment and civil liberties

```{r tbl-e2c}
# Build nicer column names
models_for_table_e2c <- models %>% 
  filter(outcome_var == "Private civil liberties") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

# Make a named vector of original model names and nice names
model_names_tbl_e2c <- models_for_table_e2c %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e2c$model)

# Rename the columns
names(models_tbl_e2c) <- recode(names(models_tbl_e2c), !!!model_names_tbl_e2c)

modelsummary(models_tbl_e2c,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r plot-coefs-e2c}
coef_plots <- models %>% 
  filter(model == "m_clpriv_v2csreprss") %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

```{r plot-mfx-e2c}
mfx <- models %>% 
  filter(model == "m_clpriv_v2csreprss") %>% 
  mutate(plot_vars = "v2csreprss") %>% 
  mutate(fx = map2(actual_model, plot_vars, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Civil society repression\n(higher values = less repression)",
       y = "Predicted civil liberties index\n(higher values = less violence)") +
  theme_ngo()
```

# E~2d~: Civil society environment and latent physical integrity rights

```{r tbl-e2d}
# Build nicer column names
models_for_table_e2d <- models %>% 
  filter(outcome_var == "Latent human rights") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

# Make a named vector of original model names and nice names
model_names_tbl_e2d <- models_for_table_e2d %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e2d$model)

# Rename the columns
names(models_tbl_e2d) <- recode(names(models_tbl_e2d), !!!model_names_tbl_e2d)

modelsummary(models_tbl_e2d,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r plot-coefs-e2d}
coef_plots <- models %>% 
  filter(model == "m_lhr_v2csreprss") %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

```{r plot-mfx-e2d}
mfx <- models %>% 
  filter(model == "m_lhr_v2csreprss") %>% 
  mutate(fx = map2(actual_model, "v2csreprss",
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

>>>>

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(here)

@@

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
             m_lhr_baseline, m_lhr_v2csreprss))

  # Load regression tables
  tar_load(c(models_tbl_e2a, models_tbl_e2b))

@@

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = "none", alpha = "none") +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

# E~2b~: Civil society environment and latent physical integrity rights

```{r tbl-e2b}
# Build nicer column names
models_for_table_e2b <- models %>% 
  filter(outcome_var == "Latent human rights") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

@@

```{r plot-coefs-e2b}
coef_plots <- models %>% 
  filter(model == "m_lhr_v2csreprss") %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = "none", alpha = "none") +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

```{r plot-mfx-e2b}
mfx <- models %>% 
  filter(model == "m_lhr_v2csreprss") %>% 
  mutate(fx = map2(actual_model, "v2csreprss",
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)
